CommonMind Consortium: DLPFC

### 2020-10-12 combined_analysis/combine_all_DLPFC_by_celltype.Rmd
initial commit

```{r create.voom}

vobj.lst = lapply( levels(METADATA$Cohort), function(chrt){

@@

### Test marginals for Scz vs controls
```{r differential.expression.simple}
form.lst = list(
  `MSSM-Penn-Pitt`  = ~ Dx + Reported_Gender + RIN +scale(IntronicRate) + scale(IntragenicRate) + scale(IntergenicRate) + scale(rRNARate) + InstitutionageOfDeath,
  `NIMH-HBCC`       = ~ Dx + Reported_Gender + RIN + scale(IntronicRate) + scale(IntragenicRate) + scale(IntergenicRate) + scale(rRNARate) + ageOfDeath)

>>>>

```{r create.voom}
vobj.lst = lapply( levels(METADATA$Cohort), function(chrt){

@@

### Test marginals for Scz vs controls
```{r differential.expression.simple}
form.lst = list(
  `MSSM-Penn-Pitt`  = ~ Dx + Reported_Gender + RIN +scale(IntronicRate) + scale(IntragenicRate) + scale(IntergenicRate) + scale(rRNARate) + Institution*ageOfDeath,
  `NIMH-HBCC`       = ~ Dx + Reported_Gender + RIN + scale(IntronicRate) + scale(IntragenicRate) + scale(IntergenicRate) + scale(rRNARate) + ageOfDeath)
